%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Fall 2012.  
%  For more info about this template or the 
%  TAMU LaTeX User's Group, see http://www.howdy.me/.
%
%  Author: Wendy Lynn Turner 
%	 Version 1.0 
%  Last updated 8/5/2012
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                           ACKNOWLEDGEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{ACKNOWLEDGEMENTS}
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENTS}  % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.

I want to start by thanking my parents, Gary and Susan McGee, for their
support and encouragemet over the years.
%
They laid the foundation of my education.
%
I am grateful to my advisor, Dr. Caverlee, for everything he did to support my
research.
%
He taught me to research, to analyze data, and how to really read a reasearch
paper.
%
Jeremy Kelly introduced me to Infolab, and founded a handful of companies
that employed me on and off during my years of graduate school.
%
His mentorship made me a better software developer.
%
I'd like to thank Brian Eoff for building the Twitter Streaming API client that
downloaded the initial set of geo-located Tweets.
%
Zhiyaun Cheng deserves credit for his work on the problem of location detection
and for reccomending quite a few papers to me.
%
Many thanks to Krishna Kamath, Elham Khabiri, Kyumin Lee, Yuan Liang, and the
rest of Infolab.
%
And finally, my thanks are due to my awesome wife Keri Bean.
%
Her love and encouragement helped me to finish this journey.
\pagebreak{}
