\flchap{Conclusion}

%After you ship it, you should also expand the conclusion to include more
%thoughts on what we have learned and next steps.
%Give us a vision of the future.

In this thesis, we have demonstrated that some types of relationships tend to
be closer than others.
%
Some features of relationships are correlated with physical proximity.
%
For example, users with lots of followers tend to be distant, while users who
mention each other tend to be closer.
%
In general, users with stronger ties tend to be local.
%
We used this to accurately predict the locations of users on a social media
website.

There are two general directions that the future work on this research could
go: improving the results of the prediction and using the predicted locations
to build systems.
%
One way to improve this predictor is to combine tie strength and the social
graph with other factors such as the words users choose to use as described by
Cheng \cite{cheng2010you}.
%
It could be useful for the predictor to return not just a location, but an
estimate of the quality of the prediction.
%
The system described in this thesis only considered users who have a
well-defined location.
%
FriendlyLocation could be modified to identify users who do not have meaningful
locations such as people who constantly travel and accounts that represent
large organizations.
%
% WAT?
%This could work well with the node locality metric which is defined by
%Scellato\cite{scellato2010distance}.

Finally, high-quality geographic information opens up new avenues for research
and software engineering.
%
Location prediction will allow websites to provide hyper-local content and
services.
%
For example, the distance between a pair of users could be considered when
suggesting new friends on a social network and websites will be able to give
users more accurate, localized search results.

The idea that started our research into location prediction was community crowd
detection.
%
With geographic location of users, we can cluster users and find local
conversations.
%
These conversations can be analyzed to understand local political and social
events.
%
Location prediction will allow us to create a more clear picture of the
conversations in a community.
