\documentclass{sig-alternate}
\usepackage{url}

\begin{document}

\conferenceinfo{WWW'13,} {May 13--17, 2013, Rio de Janeiro, Brazil}
\CopyrightYear{2013}
\crdata{978-1-4503-0717-8/11/10}
\clubpenalty=10000
\widowpenalty = 10000

\numberofauthors{1}
\author{
\alignauthor
For blind review
}



\title{Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX
Format\titlenote{(Produces the permission block, and
copyright information). For use with
SIG-ALTERNATE.CLS. Supported by ACM.}}
\subtitle{[Extended Abstract]
\titlenote{A full version of this paper is available as
\textit{Author's Guide to Preparing ACM SIG Proceedings Using
\LaTeX$2_\epsilon$\ and BibTeX} at
\texttt{www.acm.org/eaddress.htm}}}

\maketitle
\begin{abstract}

With the rise of volunteered user location information through services
like Foursquare, Google Latitude, and Facebook Places, we face unprecedented
access to the real-world connections among millions of social media users.
%
This location information is increasingly incorporated into social media for
providing localized content, location-aware recommendations, and other
geo-spatial enabled services.
%
In this paper, we investigate the relationship between the strength of the tie
between a pair of users, and the distance between the pair through an
examination of over 100 million geo-encoded tweets and
over 73 million user profiles collected from Twitter.
%
Based on this investigation, we identify several factors such as number of
followers and how the users interact that can strongly reveal the distance
between a pair of users, and use these factors to train a tree classifier to
predict the distance between a pair of connected users.
%
We use the results of this classifier as the input to a maximum likelihood
estimator to predict a user's location.
%
We find that this proposed method significantly improves the results of
location estimation relative to a state-of-the-art technique.


\end{abstract}

% FIXME: this junk
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging}

\input{section1}
\input{section2}
\input{section3}
\input{section4}
\input{section5}
\input{conclusion}

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{fl}
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
\end{document}
